Heavy inextensible strings in the Schwarzschild geometry

### 2024-11-05 weighted_string.Rmd
mathematica screenshot

which gives an expression for $r''(\phi)$.  In R idiom, this is:

```{r definerdashdash}
rdashdash <- function(r,rdash,lambda,M=1/2){
    x <- sqrt(1-2*M/r)
    return(
    (
        M*(4+lambda*(4-3*x))*r^2 +
        (-1+lambda*(-1+x))*r^3 +
        M*(3 + lambda*(3-2*x))*rdash^2 +
        2*r*(M^2*(-2+lambda*(-2+x)) + (-1+lambda*(-1+x))*rdash^2)
    ) / (
        (-1+lambda*(-1+x))*r*(-2*M+r)
    )
    )
}
```

>>>>

which gives an expression for $r''(\phi)$.

![Mathematica screenshot](mathematica_screenshot.png)

In R idiom, this is:

```{r definerdashdash}
rdashdash <- function(r,rdash,lambda,M=1/2){
    x <- sqrt(1 - 2*M/r)
    return(
    (
        M*(4 + lambda*(4 - 3*x))*r^2 +
        (-1 + lambda*(-1 + x))*r^3 +
        M*(3 + lambda*(3 - 2*x))*rdash^2 +
        2*r*(M^2*(-2 + lambda*(-2 + x)) + (-1 + lambda*(-1 + x))*rdash^2)
    ) / (
        (-1 + lambda*(-1 + x))*r*(-2*M + r)
    )
    )
}
```
